Better fusion for filters

### 2014-04-07 2014betterfusionforfilters/section/02-CNF.tex
ok
Rework introduction
suggest normalise2 for better motivating program?
Add diagrams for normalize2 example

@@

It is important to note, however, that because of the purity of Haskell, we are free to take certain liberties when reordering the program.
None of the worker functions, nor any @external@ computations may produce visible side-effects; the only observable effect must be to produce their output.
\input{figures/Program.tex}

>>>>

%!TEX root = ../Main.tex
%\eject

\begin{figure*}[ht!]
\begin{center}
\includegraphics[scale=0.5]{figures/ex1-compare.pdf}
\end{center}

\caption{Clusterings for normalize2 example: with stream fusion; our system; best imperative system}
\label{f:normalize2-cluterings}
\end{figure*}

@@

It is important to note that because of the purity of Haskell, we are free to take certain liberties when reordering the program.
None of the worker functions, nor any @external@ computations may produce visible side-effects; the only observable effect must be to produce their output.
\input{figures/Program.tex}
